Resolvable Ambiguity

### 2019-07-05 paper/paper.tex
Some more related work

>>>>

The detection of classical ambiguity in context-free grammars is undecidable in general \cite{cantorAmbiguityProblemBackus1962}, yet numerous heuristic approaches exist. Examples include linguistic characterizations and regular language approximations \cite{brabrandAnalyzingAmbiguityContextFree2007}, using sat-solvers \cite{axelssonAnalyzingContextFreeGrammars2008}, and other conservative approaches \cite{schmitzConservativeAmbiguityDetection2007}, For an overview, and additional approaches, see the PhD thesis of \citet{bastenAmbiguityDetectionProgramming2011}.
